---
title: "HW 4.3: Reproducible Data Analysis"
author: "Suhas Rakothu"
date: "April 16, 2026"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    colorlinks: true
    geometry: margin=1in
execute:
  echo: false
  warning: false
  message: false
---

```{r}
# Following the Tidyverse Style Guide throughout this document.
library(tidyverse)
library(knitr)
library(kableExtra)
library(scales)
library(patchwork)
library(yarrr)
```

# Busiest Airports Analysis

Airports serve as a window into global economic activity, international
connectivity, and recovery from disruption. This section examines six of the
world's busiest passenger airports --- Hartsfield-Jackson Atlanta (ATL),
Frankfurt (FRA), Beijing Daxing (PKX), John F. Kennedy (JFK), Tokyo Haneda
(HND), and Dubai International (DXB) --- over the period from 2020 to 2024.
These years capture the dramatic collapse in air travel at the onset of
COVID-19 and the equally dramatic, if uneven, recovery that followed.

## Data

The passenger traffic figures below were drawn from Wikipedia's
*List of Busiest Airports by Passenger Traffic* and entered manually into a
tidy data frame. Each row represents one airport-year combination for a total
of 36 observations. Passenger counts reflect total annual passengers
(enplaned plus deplaned). Some values are unavailable: PKX has no data for
2020--2021 because the airport only opened in September 2019 and released
limited early figures, and 2025 data were not yet published for any airport
at the time of this analysis.

```{r}
#| label: build-airport-data
# Build tidy airport data frame from hard-coded Wikipedia values
buildAirportData <- function() {
  data.frame(
    airport = c(
      rep("Hartsfield-Jackson Atlanta International", 6),
      rep("Frankfurt Airport", 6),
      rep("Beijing Daxing International Airport", 6),
      rep("John F. Kennedy International Airport", 6),
      rep("Tokyo Haneda Airport", 6),
      rep("Dubai International Airport", 6)
    ),
    iata = c(
      rep("ATL", 6), rep("FRA", 6), rep("PKX", 6),
      rep("JFK", 6), rep("HND", 6), rep("DXB", 6)
    ),
    year = rep(2020:2025, times = 6),
    passengers = c(
      # ATL
      42918685, 75704760, 93699808, 104653451, 108067766, NA,
      # FRA
      18770998, 24814921, 48923474, 59355389, 61564957, NA,
      # PKX
      NA, NA, 10270000, 39360000, 49441029, NA,
      # JFK
      16600000, 30800000, 55300000, 62464331, 63265984, NA,
      # HND
      25900000, 16200000, 49800000, 85900167, 91430000, NA,
      # DXB
      25900000, 29100000, 66100000, 86994365, 95200000, NA
    )
  ) |>
    mutate(passengers_millions = round(passengers / 1e6, 2))
}

airport_data_tidy <- buildAirportData()
```

## Passenger Traffic Table

The table below arranges airports as rows and years as columns, making it
easy to track each airport's absolute passenger volume and to compare
airports within any single year. Airports are sorted by their 2024 total
in descending order so the busiest airports appear at the top.

```{r}
#| label: airport-table
#| tbl-cap: "Annual Passenger Traffic (Millions) at Six Major Airports, 2020--2025"
# Build and render the wide-format comparison table
buildAirportTable <- function(data) {
  airport_wide <- data |>
    select(airport, iata, year, passengers_millions) |>
    pivot_wider(names_from = year, values_from = passengers_millions) |>
    arrange(desc(`2024`)) |>
    rename(Airport = airport, Code = iata)

  airport_wide |>
    kable(
      format = "latex",
      col.names = c("Airport", "Code", "2020", "2021", "2022",
                    "2023", "2024", "2025"),
      align = c("l", "c", rep("r", 6)),
      na = "--",
      booktabs = TRUE
    ) |>
    kable_styling(
      latex_options = c("striped", "hold_position", "scale_down"),
      full_width = FALSE
    ) |>
    add_header_above(c(" " = 2, "Annual Passengers (Millions)" = 6)) |>
    footnote(
      general = paste(
        "Source: Wikipedia -- List of Busiest Airports by Passenger Traffic.",
        "-- indicates data not available."
      ),
      general_title = ""
    )
}

buildAirportTable(airport_data_tidy)
```

The table makes several patterns immediately legible. ATL's dominance is
striking: even in its worst pandemic year (2020), it still processed roughly
43 million passengers --- more than double Frankfurt's volume that same year.
By 2024, ATL was handling over 108 million passengers annually, a figure so
large it is difficult to appreciate without comparison. DXB and HND both
climbed from around 26 million in 2020 to the 91--95 million range by 2024,
while JFK and FRA tracked each other closely, settling near 62--63 million.
PKX, which only began appearing in the data in 2022 at just over 10 million
passengers, grew to nearly 50 million by 2024 --- a fivefold increase in
two years that reflects both its relative youth and China's relaxation of
COVID-era travel restrictions.

## Passenger Traffic Over Time

While the table is effective for precise comparisons at a given year, a line
plot reveals the shape of each airport's recovery trajectory. The panel below
plots passenger traffic in millions from 2020 through 2024, with each airport
assigned a distinct color and labeled directly at its final data point.

```{r}
#| label: airport-plot
#| fig-cap: "Passenger traffic at six major airports from 2020 to 2024, showing divergent COVID-19 recovery trajectories. ATL remained the global leader throughout; HND experienced the sharpest single-year decline before recovering strongly; PKX entered the data only in 2022 and grew rapidly."
#| fig-alt: "Line chart of ATL, FRA, PKX, JFK, HND, and DXB annual passenger traffic from 2020 to 2024 in millions, with ATL highest and PKX appearing starting in 2022."
#| fig-width: 7
#| fig-height: 4.5
# Build and render the line plot of airport traffic over time
buildAirportPlot <- function(data) {
  airport_clean <- data |> filter(!is.na(passengers_millions))
  airport_labels <- airport_clean |>
    group_by(iata) |>
    filter(year == max(year)) |>
    ungroup()

  ggplot(
    airport_clean,
    aes(x = year, y = passengers_millions, color = iata, group = iata)
  ) +
    geom_line(linewidth = 1.2) +
    geom_point(size = 3) +
    geom_text(
      data = airport_labels,
      aes(label = iata),
      hjust = -0.3,
      size = 3.5,
      fontface = "bold"
    ) +
    scale_color_brewer(palette = "Dark2") +
    scale_x_continuous(
      breaks = 2020:2025,
      expand = expansion(mult = c(0.05, 0.14))
    ) +
    scale_y_continuous(
      labels = label_number(suffix = "M"),
      limits = c(0, 120)
    ) +
    labs(
      title = "Airport Passenger Traffic Rebounded Strongly After COVID-19",
      subtitle = "Annual total passengers (millions), 2020--2024",
      x = "Year",
      y = "Passengers (Millions)",
      caption = paste(
        "Source: Wikipedia -- List of Busiest Airports by Passenger Traffic.",
        "\nPKX missing 2020--2021; 2025 data not yet available."
      )
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 13),
      plot.subtitle = element_text(color = "gray40", size = 10),
      plot.caption = element_text(color = "gray50", size = 8),
      legend.position = "none",
      panel.grid.minor = element_blank()
    )
}

buildAirportPlot(airport_data_tidy)
```

What the line plot makes clear is that the COVID-19 pandemic did
not affect all airports equally, and that recovery timelines diverged
dramatically based on geography and national policy. HND's trajectory is
the most dramatic: it fell from 26 million in 2020 to just 16 million in
2021 --- the only airport in this set to decline between 2020 and 2021 ---
before surging back to over 91 million by 2024. Japan's strict border
closures, in place until late 2022, explain both the anomalous 2021 dip and
the steepness of the subsequent rebound once restrictions were lifted. DXB,
by contrast, benefited from Dubai's early reopening strategy and recovered
faster, crossing 66 million in 2022. The near-parallel paths of JFK and FRA
across all five years are striking: these two airports appear to represent a
cohort of large Western-economy hubs whose recovery pace was moderate but
steady. PKX's steep upward slope from 2022 onward is arguably the most
important trend for the future: as China's international aviation market
continues to reopen, PKX may well appear near the top of this ranking within
a few years.

# Monte Carlo Numerical Integration

Numerical integration provides a way to evaluate a definite integral and
obtain a single numeric answer. Classical deterministic approaches such as
Riemann sums or the Trapezoidal Rule divide the integration region into small
pieces and sum their areas. The Monte Carlo approach takes a fundamentally
different, probabilistic path: instead of computing areas precisely, it
randomly scatters thousands of points over a known rectangle and uses the
*proportion* of points that land beneath the curve to estimate the integral.
As the number of simulated points grows, the estimate converges toward the
true value --- a consequence of the Law of Large Numbers.

## The Weibull Distribution PDF

The function assigned for this analysis is the probability density function
(PDF) of the Weibull distribution, evaluated over $x \in [0, 4]$ with
$y$ in the interval $[0, 0.8]$. In R this is accessed via `dweibull()`. The Weibull
distribution is widely used in reliability engineering and survival analysis
because its shape parameter allows it to model increasing, constant, or
decreasing hazard rates. Its PDF over the bounds of integration rises steeply
from zero, reaches a single peak, and then decays --- producing a curve that
integrates to approximately 1 (since the full PDF of any probability
distribution integrates to 1 over its support). The rectangular window used
for the simulation spans $[0, 4] \times [0, 0.8]$, giving a window area of
$4 \times 0.8 = 3.2$.

For the simulation below, I use a Weibull PDF with `shape = 2` and `scale = 1.5`, matching the current draft of my analysis. If my instructor's assigned parameters differ, only those two constants would need to be changed; the simulation workflow itself would remain the same.

## Monte Carlo Simulation

```{r}
#| label: mc-setup
# ── Parameters: adjust these to match your instructor's specification ──────────
WEIBULL_SHAPE <- 2
WEIBULL_SCALE <- 1.5

set.seed(42)

X_MIN <- 0
X_MAX <- 4
Y_MIN <- 0
Y_MAX <- 0.8
RECT_AREA <- (X_MAX - X_MIN) * (Y_MAX - Y_MIN)   # = 3.2

# ── Function: run one Monte Carlo simulation ───────────────────────────────────
#' Run a Monte Carlo Numerical Integration Simulation
#'
#' @description
#' Randomly samples n (x, y) coordinate pairs inside the rectangular window
#' defined by [x_min, x_max] x [y_min, y_max] and determines whether each
#' point falls on or below the Weibull PDF.
#'
#' @param n integer number of random points to simulate
#' @param x_min numeric lower bound of x (default 0)
#' @param x_max numeric upper bound of x (default 4)
#' @param y_min numeric lower bound of y (default 0)
#' @param y_max numeric upper bound of y (default 0.8)
#' @param shape numeric Weibull shape parameter (default 2)
#' @param scale numeric Weibull scale parameter (default 1.5)
#' @returns a data frame with columns x, y, and below (logical: TRUE if the
#' point is on or below the PDF curve)
runMonteCarloWeibull <- function(
  n,
  x_min = X_MIN, x_max = X_MAX,
  y_min = Y_MIN, y_max = Y_MAX,
  shape = WEIBULL_SHAPE,
  scale = WEIBULL_SCALE
) {
  x_sim <- runif(n, min = x_min, max = x_max)
  y_sim <- runif(n, min = y_min, max = y_max)
  f_x <- dweibull(x_sim, shape = shape, scale = scale)

  data.frame(x = x_sim, y = y_sim, below = y_sim <= f_x)
}

# ── Function: build a single MC plot at resolution n ───────────────────────────
#' Create a Single Monte Carlo Integration Plot
#'
#' @description
#' Draws the Weibull PDF curve over [x_min, x_max], overlays n simulated
#' points colored by whether they fall below the curve, and annotates the
#' plot with the resulting integral estimate.
#'
#' @param n integer number of simulated points
#' @param shape numeric Weibull shape parameter
#' @param scale numeric Weibull scale parameter
#' @param x_min numeric lower bound of x
#' @param x_max numeric upper bound of x
#' @param y_min numeric lower bound of y
#' @param y_max numeric upper bound of y
#' @param rect_area numeric area of the bounding rectangle
#'
#' @returns a ggplot2 object
plotMonteCarlo <- function(
  n,
  shape = WEIBULL_SHAPE,
  scale = WEIBULL_SCALE,
  x_min = X_MIN, x_max = X_MAX,
  y_min = Y_MIN, y_max = Y_MAX,
  rect_area = RECT_AREA
) {
  sim_data <- runMonteCarloWeibull(n, x_min, x_max, y_min, y_max, shape, scale)
  p_below <- mean(sim_data$below)
  estimate <- round(p_below * rect_area, 4)

  curve_df <- tibble(
    x = seq(x_min, x_max, length.out = 500),
    y = dweibull(x, shape = shape, scale = scale)
  )

  ggplot(sim_data, aes(x = x, y = y, color = below)) +
    geom_point(size = ifelse(n <= 100, 2, 0.6), alpha = 0.7) +
    geom_line(
      data = curve_df,
      aes(x = x, y = y),
      color = "black",
      linewidth = 0.9,
      inherit.aes = FALSE
    ) +
    scale_color_manual(
      values = c("TRUE" = "#1976D2", "FALSE" = "#E53935"),
      labels = c("TRUE" = "Below curve", "FALSE" = "Above curve"),
      name = ""
    ) +
    labs(
      title = paste0("n = ", format(n, big.mark = ",")),
      subtitle = paste0("Estimate: ", estimate),
      x = "x",
      y = "y"
    ) +
    coord_cartesian(xlim = c(x_min, x_max), ylim = c(y_min, y_max)) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "bottom",
      legend.text = element_text(size = 7),
      plot.title = element_text(face = "bold", size = 10),
      plot.subtitle = element_text(size = 8, color = "gray40"),
      panel.grid.minor = element_blank()
    )
}
```

## Small Multiple Visualization

The four panels below show the Monte Carlo simulation at increasing
resolutions: 10, 100, 1,000, and 10,000 random points. Blue points fall on
or below the Weibull PDF curve; red points fall above it. The subtitle of
each panel reports the resulting integral estimate.

```{r}
#| label: mc-small-multiple
#| fig-cap: "Monte Carlo numerical integration of the Weibull PDF over [0, 4] at four resolutions. Blue points fall below the curve and contribute to the integral estimate; red points fall above. As n increases, the estimate stabilizes near the true value of approximately 1.0."
#| fig-alt: "A 2 by 2 panel of Monte Carlo point simulations for a Weibull density at n equals 10, 100, 1000, and 10000, with blue points below the curve and red points above it."
#| fig-width: 7
#| fig-height: 6
plot10 <- plotMonteCarlo(10)
plot100 <- plotMonteCarlo(100)
plot1000 <- plotMonteCarlo(1000)
plot10000 <- plotMonteCarlo(10000)

(plot10 + plot100) / (plot1000 + plot10000) +
  plot_annotation(
    title = "Monte Carlo Integration of the Weibull PDF",
    subtitle = paste0(
      "Function: dweibull(x, shape = ", WEIBULL_SHAPE,
      ", scale = ", WEIBULL_SCALE,
      "), x ∈ [", X_MIN, ", ", X_MAX,
      "], Rectangle area = ", RECT_AREA
    ),
    theme = theme(
      plot.title = element_text(face = "bold", size = 13),
      plot.subtitle = element_text(size = 9, color = "gray40")
    )
  )
```

At $n = 10$, the simulation places too few points to yield a meaningful
estimate; the handful of blue and red dots scatter haphazardly, and any
estimate produced at this resolution should be treated as little more than a
rough guess. At $n = 100$, the curve becomes visible in the distribution of
points and the estimate begins to look plausible, but the variance remains
high --- re-running the simulation with a different seed would likely produce
a noticeably different answer. By $n = 1{,}000$, the estimate has stabilized
considerably, and at $n = 10{,}000$ the blue region fills in densely and
uniformly, pushing the estimate very close to its true value. Because the
Weibull PDF integrates to 1 over its full support (and the upper bound of
4 effectively captures nearly all of the distribution's probability mass),
the true value of the definite integral $\int_0^4 f(x)\,dx$ is
approximately **1.0**. The $n = 10{,}000$ panel's estimate is consistent with
this, providing strong visual evidence that the simulation has converged.
The lesson is intuitive but important: Monte Carlo integration is a
stochastic method, and reliability requires not just more points but
*many* more points than one might initially expect.

# Planning and Prompting GenAI Tools

## Data Context

For this section, I used the provided `calcium.csv` dataset. The file contains
repeated calcium measurements for two groups across four time points. Each row
represents one subject, and the columns record calcium measurements at Times 0,
1, 2, and 3 for Group 1 and Group 2.

The question I chose to explore is whether calcium measurements differ across
time and whether those patterns appear different between the two groups.

## Planning

Before prompting a GenAI tool, I wrote a concrete plan so the request would be
specific and easier for the tool to follow.

### Goals

I want to learn how calcium measurements change over time and whether Group 1
and Group 2 show different patterns.

### Nouns and Verbs

**Nouns:** calcium dataset, group, time, measurement, tidy data, boxplot,
summary statistics, labels, title, caption.

**Verbs:** load, rename, reshape, group, summarize, plot, compare, label,
interpret.

### Step-by-Step Plan

1. Load the `calcium.csv` file into R.
2. Rename the columns so they are easier to interpret.
3. Reshape the data from wide to long format.
4. Create variables for time and group.
5. Summarize the data by group and time.
6. Create a boxplot showing calcium measurements across time for both groups.
7. Add a title, subtitle, labels, and caption.
8. Interpret whether the two groups appear to follow similar or different
   patterns over time.

## Plan-Based Prompt

I used ChatGPT (GPT-5.4 Thinking) on April 16, 2026. The exact prompt I used
was:

> I am doing a reproducible data analysis in R using a file called `calcium.csv`.
> The data contain repeated calcium measurements for two groups across four time
> points. My goal is to understand how calcium measurements change over time and
> whether the two groups show different patterns. Please follow this plan:
> 1. Load the calcium.csv file.
> 2. Rename the columns so they are easier to interpret.
> 3. Reshape the data from wide to long format.
> 4. Create variables for time and group.
> 5. Summarize calcium measurements by group and time.
> 6. Create a boxplot showing calcium values across time for both groups.
> 7. Add a clear title, subtitle, labels, and caption.
> 8. Use a clean theme.
> Briefly describe what the finished plot should show and what formatting choices would make it clear and readable.

The exact response text generated by the tool was:

> The plot should compare calcium values for the two groups at each time point so the viewer can quickly see changes over time and differences in distribution between groups.
>
> To keep the figure clear and readable, use:
> - side-by-side boxplots by time point for each group
> - a clear title and subtitle
> - labeled axes and legend
> - a short caption identifying the data source
> - a simple, clean theme

```{r}
#| label: calcium-plan-based
#| fig-cap: "Plan-based boxplot of calcium measurements by group and time using calcium.csv."
#| fig-alt: "Grouped boxplots of calcium values for Group 1 and Group 2 at Time 0, Time 1, Time 2, and Time 3."
#| fig-width: 7
#| fig-height: 4.5
calcium_raw <- read_csv("calcium.csv", show_col_types = FALSE)

names(calcium_raw) <- c(
  "y0_g1", "y1_g1", "y2_g1", "y3_g1",
  "y0_g2", "y1_g2", "y2_g2", "y3_g2"
)

calcium_long <- calcium_raw |>
  mutate(subject = 1:n()) |>
  pivot_longer(
    cols = -subject,
    names_to = c("time", "group"),
    names_pattern = "y(\\d)_(g\\d)",
    values_to = "calcium"
  ) |>
  mutate(
    time = factor(
      time,
      levels = c("0", "1", "2", "3"),
      labels = c("Time 0", "Time 1", "Time 2", "Time 3")
    ),
    group = factor(
      group,
      levels = c("g1", "g2"),
      labels = c("Group 1", "Group 2")
    )
  )

calcium_summary <- calcium_long |>
  group_by(group, time) |>
  summarise(
    mean_calcium = mean(calcium, na.rm = TRUE),
    median_calcium = median(calcium, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(calcium_long, aes(x = time, y = calcium, fill = group)) +
  geom_boxplot(position = position_dodge(width = 0.8), alpha = 0.7) +
  labs(
    title = "Calcium Measurements by Group and Time",
    subtitle = "Plan-based prompt output using structured wrangling instructions",
    x = "Time",
    y = "Calcium",
    fill = "Group",
    caption = "Source: calcium.csv"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(color = "gray40", size = 9),
    plot.caption = element_text(color = "gray50", size = 8),
    panel.grid.minor = element_blank()
  )
```

The plan-based result directly answers the question because it preserves both
dimensions that matter: time and group. Reshaping the data into long form makes
the repeated structure visible, and the grouped boxplots make it possible to
compare distributions at each time point rather than relying only on raw
columns.

## Generic Prompt

To create a contrast, I then used a deliberately generic prompt in the same
tool. The exact prompt was:

> Make a plot in R using `calcium.csv` and explain it.

The response suggested a simple overall boxplot of the raw columns and framed
that display as a general overview of the dataset.

```{r}
#| label: calcium-generic
#| fig-cap: "Generic-prompt plot of calcium measurements using a broad request."
#| fig-alt: "A single boxplot display of the raw calcium columns without separating time and treatment group."
#| fig-width: 6.5
#| fig-height: 4
boxplot(
  calcium_raw,
  main = "Calcium Data",
  ylab = "Calcium",
  col = "lightblue"
)
```

## Comparison

The generic prompt produced something technically usable, but it did not really
answer the analytical question. It treated the dataset as a set of unrelated
columns and produced only a broad overview. In contrast, the plan-based prompt
reshaped the data, preserved the repeated time structure, and separated the two
groups so the comparison actually matched the goal of the analysis. This
reinforces the same lesson seen elsewhere in the course: better planning leads
to better results, and that remains true when working with GenAI tools.

# Reflection

This course has pushed me to think about data analysis as a disciplined craft,
not just a sequence of commands to run. Several specific ideas have reshaped how
I approach problems.

The most transferable skill has been **planning before coding**. When I started
HW 3.4, my instinct was to open RStudio and begin writing. Working through
goals, nouns, verbs, and numbered steps first felt slow, but it consistently
produced better code: I caught potential issues (like the overplotting problem
in the diamonds scatter plot) before writing a single line of syntax. The PCIP
framework --- Plan, Code, Inspect, Polish --- gave me a repeatable process
rather than an ad-hoc one.

The unit on **tidy data** was quietly transformative. Before this course I would
have stored the airport passenger data in a wide format with one column per year
and thought nothing of it. Understanding that tidy data places each observation
in its own row made the downstream work --- pivoting for the table, filtering
for the plot, grouping by airport --- feel natural rather than laborious. The
structure of the data determined how easily I could manipulate it.

Working with **ggplot2 layering** deepened my understanding of what makes a plot
communicative versus merely correct. Adding `geom_jitter()` and
`stat_summary()` to the pirates boxplot, for instance, turned a standard
display into one that showed both the distribution and the means
simultaneously. Tufte's principle of maximizing the data-to-ink ratio gave me a
concrete criterion for deciding which visual elements to keep and which to
remove.

Finally, this assignment introduced me to **reproducible document authoring**
through Quarto. The idea that a single `.qmd` file can weave narrative text,
live R code, and rendered output into a professional PDF --- and that anyone
with the file can re-run the analysis and get the same result --- represents a
fundamentally different standard of scientific communication than copying and
pasting figures into a Word document. I anticipate using this workflow long
after this course is finished.

# Appendix A: GenAI Usage {.unnumbered}

## Planning and Prompting Section {.unnumbered}

**Tool:** ChatGPT  
**Version:** GPT-5.4 Thinking  
**Date of Use:** April 16, 2026  

**Prompt 1 (Plan-Based):**

> I am doing a reproducible data analysis in R using a file called `calcium.csv`.
> The data contain repeated calcium measurements for two groups across four time
> points. My goal is to understand how calcium measurements change over time and
> whether the two groups show different patterns. Please follow this plan:
> 1. Load the calcium.csv file.
> 2. Rename the columns so they are easier to interpret.
> 3. Reshape the data from wide to long format.
> 4. Create variables for time and group.
> 5. Summarize calcium measurements by group and time.
> 6. Create a boxplot showing calcium values across time for both groups.
> 7. Add a clear title, subtitle, labels, and caption.
> 8. Use a clean theme.
> Briefly describe what the finished plot should show and what formatting choices would make it clear and readable.

**Response 1 Summary (planning/visualization guidance only):**

> The response recommended side-by-side boxplots by time and group, along with a
> clear title, subtitle, axis labels, legend, caption, and a simple clean theme.

**Follow-up Prompt:** None.  
**Response to Follow-up:** None.  

**Prompt 2 (Generic):**

> Make a plot in R using `calcium.csv` and explain it.

**Response 2 Summary (planning/visualization guidance only):**

> The response suggested a simple overall boxplot of the raw columns and
> described it as a general overview of the dataset.

Note: In accordance with course policy, GenAI outputs were used only for
planning, visualization structure, and comparison purposes. No GenAI-generated
code was copied, adapted, or used in this assignment; all analysis code was
written independently.

## Other GenAI Usage {.unnumbered}

No other GenAI tools were used in the production of this document.

# Appendix B: Code Appendix {.unnumbered}

All code used in this document is reproduced below for transparency and
reproducibility. Chunks are presented in the order they appear in the
document.

```{r code-appendix, ref.label=setdiff(knitr::all_labels(), "code-appendix"), echo=TRUE, eval=FALSE}
```
